This package manager is a project I started in an effort to assist my building of an entirely open-\/source Linux system from scratch. Because I could not find any package managers to suit my needs and desires, I instead built my own. The focus of this package manager is to be small, low-\/profile, and fast.

\subsection*{News}

Any news will be added to the head of \mbox{\hyperlink{md_NEWS}{N\+E\+WS.md}}

\subsection*{Prerequisites \& Installation}

Information on prerequisites are in \mbox{\hyperlink{md_INSTALL}{I\+N\+S\+T\+A\+LL.md}}

\subsection*{Running tests}

Currently, tests are run in two forms\+: unit tests and integration tests

\subsubsection*{Unit tests}

In order to build and execute the unit-\/tests, run make unit-\/tests

from the root directory of the project. Doing so will build and execute the unit tests, and send a short summary of the results to stdout.

\subsubsection*{Integration tests}

The integration tests serve two purposes. First, they verify that your compiler created a valid product. Second, they verify that the components of the project are able to work together in order to do what we need them to.

In order to run the integration tests, run make check

This will do a couple things. First, it will build the executable if it is not up-\/to-\/date already. Second, it will run our testing scripts in order to validate the executable.

In a similar style to the unit tests, this will run a few short Python scripts in order to verify the product created by your compiler. Afterwards, it will give you a short summary describing the results of the tests.

\subsection*{Contributing}

Information on how to contribute is in \mbox{\hyperlink{md_CONTRIB}{C\+O\+N\+T\+R\+IB.md}}

\subsection*{Licensing}

Currently, this product does not ship with any additional software. Because I am not redistributing any software, I am not currently required to follow G\+PL per the libstdc++ linking exception. As for libarchive, because I am not currently distributing its source code or a compiled binary for it, its license does not have scope over this project.

That being said, I have decided to release this under the G\+P\+Lv3. For more information regarding the G\+P\+Lv3, look at the file \mbox{\hyperlink{md_LICENSE}{L\+I\+C\+E\+N\+SE.md}}

\section*{Contact me}

If you want to let me know about a bug you found, the best way is to post an Issue on Git\+Hub\+: \href{https://github.com/The2b/Pkg-Mgr/issues}{\texttt{ https\+://github.\+com/\+The2b/\+Pkg-\/\+Mgr/issues}} Ideally, you can post a description of the bug\textquotesingle{}s effects, steps to reproduce it, as well as output from the program when running at verbosity level 4.

If you have any questions, you can send an e-\/mail to me at \href{mailto:thomas.lenz96@gmail.com}{\texttt{ thomas.\+lenz96@gmail.\+com}} I recommend you put something in the subject along the lines of \char`\"{}\+Pkg-\/\+Mgr Question\char`\"{} so that I recognize it is not coming from a spam bot or anything of the like. I have a public P\+GP key out there for that e-\/mail, with the comment \char`\"{}\+General Communications\char`\"{}, if you feel the need to reach me in a secure manner. 